A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
NM
language changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
To perform this simulation of Stokesian erosion of a porous media, two
fast and accurate methods are employed---one to solve the fluid
equations and the other to integrate the eroding grains.  The fluid
equations are reformulated in terms of a boundary integral equation
(BIE)~\cite{poz1992}.  Since the boundary conditions are Dirichlet, we
use a double-layer potential formulation so that the resulting BIE is
second-kind.  This second-kind BIE is discretized with the spectrally
accurate trapezoid rule~\cite{tre-wei2014} which results in a
well-conditioned dense linear system for an unknown density function.
This linear system is solved using fast-multipole-accelerated
GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
erosion rate (shear stress) is computed with a spectrally accurate
odd-even quadrature rule~\cite{sid-isr1988}.  In addition, the pressure
and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies})
with an upsampled trapezoid rule in the fluid bulk to assist with
visualizing the effect of erosion in porous media.

@@

We validate our method on a single circular body placed symmetrically in
a pipe flow.  By artificially fixing the area of the body as a function
of time, we are able to characterize the long-time behavior of the shape
and the resulting flow and these results agree with analytical results.
Then, we compute the vorticity of erosion in multiply-connected
geometries to better characterize erosion in porous media.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
To perform this simulation of Stokesian erosion of a porous media, two
fast and accurate methods are employed---one to solve the fluid
equations and the other to integrate the eroding grains.  The fluid
equations are reformulated in terms of a boundary integral equation
(BIE)~\cite{poz1992}.  Since the boundary conditions are Dirichlet, we
use a double-layer potential formulation so that the resulting BIE is
second-kind.  This second-kind BIE is discretized with the spectrally
accurate trapezoid rule~\cite{tre-wei2014} which results in a
well-conditioned dense linear system for an unknown density function.
This linear system is solved using fast-multipole-accelerated
GMRES~\cite{saa-sch1986}.  Once the density function is computed, the
shear stress is computed with a spectrally accurate
odd-even quadrature rule~\cite{sid-isr1988}.  In addition, the pressure
and vorticity are computed in the fluid bulk (Fig.~\ref{fig:50bodies})
with an upsampled trapezoid rule in the fluid bulk to assist with
visualizing the effect of erosion in porous media.

@@

We validate our method on a single circular body placed symmetrically in
a channel flow.  By artificially fixing the area of the body as a function
of time, we are able to characterize the long-time behavior of the shape
and the resulting flow and these results agree with analytical results.
Then, we compute the vorticity of erosion in multiply-connected
geometries to better characterize erosion in porous media.
